Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-23 article.rnw
Specify that fecundity is measured in *surviving* offspring.

The data I used in this study were drawn from the work of \textcite{terry2021natural}.
The data consist of fecundity measurements for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
In this, they form essentially the standard experimental design for parameterising a species interaction model, as described by \textcite{hart2018quantify}.

>>>>

The data I used in this study were drawn from the work of \textcite{terry2021natural}.
The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
In this, they form essentially the standard experimental design for parameterising a species interaction model, as described by \textcite{hart2018quantify}.
